\tcode{Generalisation of nth_element to a range of nths}

### 2022-01-03 draft_lundberg_nth_elements.tex
fixed wrong figure label (description in text was correct)

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2022-01-02 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09. Added images for equalization example. Added example of \emph{Before} with projections and more examples. -- 
2021-12-26: Added explanatory images to the introduction. --  
2021-12-28: Rebased wording and synopsis to C++23 draft. 2021-01-02: Updated to new performance result. Clarified that complexity is expected. Misc polishing.

>>>>

\begin{tabular}{ll}
Document \#:& D2375R1\\
Date: &2022-01-03 \\
Project: & Programming Language C++ \\
Audience: & LEWG \\
Email: &\href{mailto:lundberj@gmail.com}{lundberj@gmail.com}
\end{tabular}

@@

2021-12-16: Added clarifications and more background, explanations, wording clarifications, references, summarized performance study, applications, more questions/answers. --Based on feedback and material sent to SG9 list 2021-12-09. Added images for equalization example. Added example of \emph{Before} with projections and more examples. -- 
2021-12-26: Added explanatory images to the introduction. --  
2021-12-28: Rebased wording and synopsis to C++23 draft. 2021-01-02: Updated to new performance result. Clarified that complexity is expected. Misc polishing. 2022-01-03 (Post-sg9 call): Fixed wrong figure label.
